Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-31 src/tex/ms.tex

Our second age catalog utilizes the [C/N]--age relation calibrated by \citet[][submitted]{roberts_cn_2025} for red giant branch (RGB) and red clump stars. The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry. This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun. Limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway. Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem. The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}). With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.

>>>>

Our second age catalog utilizes the [C/N]--age relation calibrated by \citet[][submitted]{roberts_cn_2025} for red giant branch (RGB) and red clump stars. The relationship relies on the mass-dependent level of mixing during first dredge-up \citep[FDU;][]{iben_stellar_1967} to map the correlation of stellar mass, and hence age, with surface chemistry. This method has the benefit of providing age estimates for luminous giants ($\log g<2.5$), which increases the sample size at larger distances from the Sun. Limitations from the efficiency of FDU mixing and the RGB age--mass relationship mean the ages are not trustworthy outside the range $1\sim10\Gyr$, but this is the age range most useful for our purposes anyway. Additional mixing effects in low-metallicity stars also prevent the relation from being applied to luminous giant and red clump stars with $\mathFeH<-0.4$; stars on the lower RGB do not suffer from this problem. 
% The median propagated uncertainty for the [C/N]-derived ages is $\sim1\Gyr$; however, as noted by \citet[][submitted]{roberts_cn_2025}, the propagated errors underestimate the true age uncertainty, so we enhance the uncertainties by 40\% (see Table \ref{tab:uncertainties}).
Following the recommendation of \citet[][submitted]{roberts_cn_2025}, we adopt a flat $1.64\Gyr$ age uncertainty for all stars.
With this relationship, we estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.
